My title

### 2024-11-19 paper/paper.qmd
update paper intro
update model and data

library(tidyverse)
library(here)
library(arrow)

analysis_data <- read_parquet(here("data/02-analysis_data/cleaned_data.parquet"))

@@

With the data obtained from @canadian_centre_for_climate_services_adjusted_2022 and @meteorological_service_of_canada_past_2023, this research paper aims to identify the factors influencing temperature at Vancouver International Airport. Located on the west coast of Richmond, the airport sits on Sea Island, surrounded by water. As a transportation hub for passengers and freight, assessing the location's safety in a warming climate is important.

@@

Why it matters paragraph

@@

# Data {#sec-data}

@@

>>>>

library(tidyverse)
library(here)
library(arrow)
library(corrplot)

analysis_data <- read_parquet(here("data/02-analysis_data/cleaned_data.parquet"))
m1 <- readRDS(here("models/mlr_1.rds"))
m2 <- readRDS(here("models/mlr_2.rds"))
glm_nolog <- readRDS(here("models/glm_nolog.rds"))
glm <- readRDS(here("models/glm_model.rds"))
brm <- readRDS(here("models/brm_model.rds"))
```

@@

With the data obtained from @canadian_centre_for_climate_services_adjusted_2022 and @meteorological_service_of_canada_past_2023, this research paper aims to identify the factors influencing temperature at Vancouver International Airport. Located on the west coast of Richmond, the airport sits on Sea Island, surrounded by water. As a transportation hub for passengers and freight, it is important to assess the location's safety in a warming climate.

@@

@@

# Data {#sec-data}
```{r}

selected_data_1 <- analysis_data[, c("wind_speed", "pressure_station", "snow", "log_mean_temp", "total_rain", "gust_speed_km_h")]
pairs(as.data.frame(selected_data_1), main = "Pairwise Scatterplots (Excluding Max Temp, and Min Temp)")
cor_matrix <- cor(selected_data_1)
print(cor_matrix)
corrplot(cor_matrix, method = "color", type = "upper", 
         tl.col = "black", tl.srt = 45, 
         col = colorRampPalette(c("blue", "white", "red"))(200))

selected_data_3 <- analysis_data[, c("wind_speed", "pressure_station", "log_mean_temp", "total_rain", "gust_speed_km_h")]
pairs(as.data.frame(selected_data_3), main = "Pairwise Scatterplots of log transformed temperature (Excluding Snow, Max Temp, and Min Temp)")
cor_matrix <- cor(selected_data_3)
print(cor_matrix)
corrplot(cor_matrix, method = "color", type = "upper", 
         tl.col = "black", tl.srt = 45, 
         col = colorRampPalette(c("blue", "white", "red"))(200))

@@

## MLR Model

```{r}
fitted_values <- fitted(m1)
ggplot(data = analysis_data, aes(x = fitted_values, y = mean_temp_F)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed", size = 1) +
  labs(x = "Predicted Temperature", y = "Actual Temperature", title = "Actual Temperature vs. Predicted Values")

```{r}
fitted_values <- fitted(m2)
ggplot(data = analysis_data, aes(x = fitted_values, y = mean_temp_F)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed", size = 1) +
  labs(x = "Predicted Temperature", y = "Actual Temperature", title = "Actual Temperature vs. Predicted Values")
```
